\prefacesection{Acknowledgments}

Getting to know Prof. Victor O.K. Li is one of my biggest fortune and the most precious part of my Ph.D. study. 
I cannot express my gratitude enough for his tremendous support and extraordinary care over the years, not only for his excellent guidance in my research, but also his exceptional encouragement and help that has strongly influenced my life. 
I still remember our first in-person conversation in Beijing before I officially started, where he told me how to solve problems and how to be an influential researcher, which I have obeyed since then.
I still remember when I wrote my first paper in 2015, he spent a week on editing my paper for 7 rounds, correcting the typos and grammatical mistakes due to my non-native English. 
I still remember that I received his endless support and encouragement every time when I got rejection and failure, which kept me keep moving towards my goal. 
I still remember his care and useful suggestions whenever I was facing difficulties in life that I did not know how to deal with.
I also remain indebted for his understanding and endless support that I could freely determine my research topics based on my interests, and I could have the chances to cooperate with talented researchers around the world.  



 I would like to thank Dr. Kyunghyun Cho who has also become so important that I cannot measure how much his guidance and support means to me during my Ph.D. research.  He was not only a good mentor, but a best friend. I visited him at NYU for 8 months, and even after that our research cooperation still continues. I am so grateful to receive his invaluable insights and suggestions every time we chat about research ideas. 
 I remain amazed that despite his busy schedule, he was always able to spare time to meet me.
 Even though sometimes we disagree with each other on certain problems, such discussion provides precious inspiration to me. 
I really appreciate his generous suggestions and help during my difficult time to determine my career path.
 

 I want to particularly thank Dr. Zhengdong Lu, for introducing me to the world of doing deep learning research. 
 When I just finished my first year Ph.D. study, 
 struggling hard by myself without anyone familiar with my interests in my department, 
 he gave me the opportunity of interning at his group in Huawei Noah's Ark Lab twice a week. 
 This opportunity completely changed the following trajectory of my research path, 
 and I started to know the ways to work on deep learning, 
 and the  important problems in the research community.
 I was also amazed by his endless interesting ideas and his knowledge on good research topics, 
and they are continuously supporting me over the years.

 I want to thank Dr. Hany Hassan for his generous care and help during my internship at the Machine Translation team of Microsoft Research. 
 It was great pleasure to work with him, and I learned a lot from his expertise in machine translation. 
 I would also like to thank James Bradbury, Dr. Richard Socher, Dr. Caiming Xiong and other members in the Salesforce Research team when I was interning there. I cannot forget all the invaluable time we spent at discussing research and life. Very special thanks to James for giving me the best courses of PyTorch and coding.
 
 I also want to thank all my paper collaborators, 
 Dr. Hang Li, 
 Dr. Graham Neubig, 
 Daniel Im,
 Baotian Hu,
 Yong Wang.
 This thesis would not have been possible without their help, support and guidance.
 
I owe a big thank-you to Dr. Ji Wu and Ping Lv when I was in Tsinghua, and to Dr. Danushka Bollegala when I was  in UTokyo, for introducing me to this amazing world of natural language processing, and for the support over the past many years.
 %I owe a big thank-you to Prof. Peter Doerschuk from the Biomedical Engineering department at Cornell, for all the encouragement and  support when I was trying to change my research field, and for telling me nothing is more important that doing things that I am happy about.  
 
During my years of Ph.D. study, I have been blessed with the friendship of many amazing people. Without them, I could not enjoy the joyful life during these years.
I want to thank all friends I met in Victor Li's group:
Ruiqiao Bai,
Miaomiao Cao,
Guanhua Chen,
Xiangyu Chen,
Xuejing Chen,
Yun Chen,
Kai Fung Chu,
Dr. Jie Chuai,
Reza Hassani Etemad,
Yang Han,
Dr. Albert Y.S. Lam,
Dr. Jacqueline Lam,
Dr. K.C. Leung,
Yan Li,
Dr. Junhao Lin,
Dr. Yi Long,
Dr. Zhiyi Lv,
Yijie Mao,
Shiguang Song,
Chenxi Sun,
Jiayao Wen,
Dr. Miles H.F. Wen,
Jiao Wang,
Yong Wang,
Dr. Jiancheng Ye,
Dr. James J.Q. Yu,
Yangwen Yu,
Qi Zhang,
Shiyao Zhang,
Xingzheng Zhu,
who provide me with a sense of a second family.
My thanks also go to so many wonderful students, researchers and professors in HKU and around the world that I have had the opportunity of befriending or learning from, including
Eneko Agirre,
Martin Arjovsky,
Danlu Chen,
Meihao Chen,
Keunwoo Choi,
Jonathan Clark,
Trevor Cohn,
Chris Dyer,
Akiko Eriguchi,
Orhan Firat,
Krzysztof Geras,
Caglar Gulcehre,
Xuejun Guo,
Yicheng Gong,
Karl Moritz Hermann,
Sebastien Jean,
Kevin Knight,
Dong Li,
Qun Liu,
Wei Liu,
Stanislas Lauly,
Xuezhe Ma,
Lili Mou,
Rodrigo Nogueira,
Alexander Rosenberg,
Xing Shi,
Yu Su,
Ilya Sutskever,
Yaohua Tang,
Zhaopeng Tu,
Jakob Uszkoreit,
Tian Wang,
Yingjie Xue,
Pengcheng Yin,
Jiakai Zhang,
Xingxing Zhang,
Jake Zhao,
Chunting Zhou,
 and many many others who I am grateful for but cannot list all their names. 
I want to specially thank my friends: Jason Lee and Zhen Li;
my best undergraduate friends: Jin Hu,  Yilin Hung and Ruochen Xu;
my old high-school friends: Xingchen Bu,  Licheng Tang, Bi Xu, and  Zhonghao Zhang;
and my nice landlords when I was in the U.S.: Jia Li and Sida Liu,
 for always encouraging me and did not leave me alone when the Ph.D. life is full of difficulty and sadness.


I want to thank Dr. Maggie Li, Dr. Kaibin Huang, and Prof. Lawrence Yeung 
for agreeing to be the examiners of my oral defense, and  helping me all the way through the thesis. %I also want to thank Prof. Olivier Gevaert for helping chair my thesis defense. 

Finally, I would like to dedicate this thesis to my beloved parents and girlfriend Lingjie for their love and never-ending support.
They have been a constant source of strength that ultimately made it possible for me to come so far. 
My debt to them is unbounded.

